---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Sebastien Lescoulie"
date: "8/29/2019"
output: 
  html_document: 
    fig_height: 6
    fig_width: 9
    highlight: espresso
    theme: cosmo
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

(it has 1846 rows and 3 columns. the 3 variables are dataset, x and y.)

### Exercise 2

The plot looks like the head of a dinosaur. The correlation ceofficient is -0.0645.

### Exercise 3


Create the data set star: 
```{r create_data-star}
star_data <- datasaurus_dozen %>% filter(dataset=="star")
```
Plot the data: 
```{r plot-star}
ggplot(data=star_data, mapping=aes(x=x, y=y))+geom_point()
```
Find the correlation coefficient:
```{r cor-star}
star_data %>% summarise(r=cor(x,y))
```
The correlation coefficient is -0.0630

### Exercise 4

Create the data set circle: 
```{r create_data-circle}
circle_data <- datasaurus_dozen %>% filter(dataset=="circle")
```
Plot the data: 
```{r plot-circle}
ggplot(data=circle_data, mapping=aes(x=x, y=y))+geom_point()
```
Find the correlation coefficient:
```{r cor-circle}
circle_data %>% summarise(r=cor(x,y))
```
The correlation coefficient is -0.0683

### Exercise 5

Plot the data: 
```{r plot-all_datasets}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")

```

Find the correlation coefficient:

```{r cor-all_datasets}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)

```


